---
title: "assigment1"
author: "idit belachsen"
date: "Tuesday, November 08, 2016"
output: html_document
---


This simple code is reading some txt data of rain events in the dead sea - their duration and their average rain depth over two near by catchments - Darga and Teqoa. Each event is classified as wither a "Cyprus Low"", a "Low to the East"" or an "Active Red Sea Trough (ARST)". In addition, each event is either associated with a flash flood in one of the catchments (marked as "1"") or not. In total, 32 rain events are associated with a flood, while 196 rain events are not. 

```{r}
library("ggplot2", lib.loc="~/R/win-library/3.1")

# reading data
dataDepthDuration = read.table("durationDepth.txt", sep="")
head(dataDepthDuration)

dat <- data.frame(X =dataDepthDuration[,'V1'],
                  Y =dataDepthDuration[,'V2'],
                  att1 = as.factor(dataDepthDuration[,'V3']),
                  att2 =as.factor(dataDepthDuration[,'V4']))

# ticks for log-scale
ticks <- c(0.1,0.5,1:10)
ooms <- 10^(0:3)
breaks <- as.vector(ticks %o% ooms)

set.seed(5)

# select the labels to show
show.labels <- c(T,T,T,T, F, F, T, F, F, F, F, T)
labels <- as.character(breaks * show.labels)
labels <- gsub("^0$", "", labels)


```

The Plot shows all events, divided to different synoptic types (different colors) and flood (filled dot) Vs. non-flood (empty dot) association 

```{r, echo=FALSE}
ggplot(dat,aes(x=X,y=Y,color=att2,shape=att2)) +geom_point(size=5, aes(fill=att2, alpha=as.character(att1))) +
  geom_point(size=5) +  
  scale_shape_manual(values=c(21,21,21),labels = c("Cyprus Low", "Low to the East","ARST"),guide = 'none') +
  scale_alpha_manual(values=c("0"=0, "1"=1),guide = 'none') +
  scale_x_log10(limits = c(0.05, NA), labels = labels, breaks = breaks) +
  scale_y_log10(limits = c(0.1, NA), labels = labels, breaks = breaks) +
  theme_bw() + theme(panel.grid.minor = element_line(color="black", linetype="dotted"), panel.grid.major = element_line(color="black", linetype="dotted")) +
  annotation_logticks(base = 10) +
  theme(legend.position="none") +
  guides(fill=FALSE)  +  scale_colour_manual('', labels = c("Cyprus Low", "Low to the East","ARST"), values = c(rgb(34, 94, 168, 150, maxColorValue=255),rgb(65,182,196, 150, maxColorValue=255),rgb(245, 177, 139, 150, maxColorValue=255))) + scale_fill_manual('', values = c(rgb(34, 94, 168, 150, maxColorValue=255),rgb(65,182,196, 150, maxColorValue=255),rgb(245, 177, 139, 150, maxColorValue=255)))+ theme(legend.text = element_text(colour="black", size = 16))+theme(legend.justification=c(0,1), legend.position=c(0,1))+theme(legend.background = element_rect(fill="white"))+
  labs(x="Event Duration [h]\n", y="Average Rain Depth [mm]") +
  theme(axis.text.x=element_text(size=20), axis.title.x=element_text(size=20),axis.text.y=element_text(size=20), axis.title.y=element_text(size=20))+
  labs(title = "Average Events Rain Amounts And Durations (Log-Scale)\n (events associated with a flood are marked as filled dots)")
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
